Parameterized convection, grid-scale clouds and resolution sensitivity in the Community Atmosphere Model

### 2019-08-07 resolution.tex
diags fig

An increasing number of atmospheric dynamical cores are being developed to maximize efficiency on massively parallel systems, permitting regionally-refined high-resolution ($\Delta x = 50$ km or less), or even globally high-resolution weather and climate simulations \citep{MPASatm,Z2014QJRMS,HETAL2016JCLIM,DCMIP16,LetAl2018JAMES}. Incorporating these advances into Atmospheric General Circulation Models (AGCMs) requires the development of physical parameterizations ({\em{physics}}) appropriate for the diversity of grid configurations that these dynamical cores are now able to support, referred to as scale-aware physics. The most common approach towards developing scale-aware physics has been through the lens of limited area, cloud resolving simulations \citep[e.g.,][]{PC2008JAS,AW2013JAS,SZ2018JCLIM}. Through subsequently filtering large-eddy simulation solutions to lower-resolution grids, a relationship between resolved and unresolved moments may be understood and ultimately parameterized. While this approach is likely necessary for developing scale-aware physics, it is not sufficient. Since the equations of motions have inherent scale dependencies, resolved dynamical modes are a function of the native grid resolution \citep{O1981JAS,WETAL1997MWR,PG2006JAS,JR2016QJRMS,J2017JAMES}. Scale-aware physics should also recognize native grid dependencies.

The sensitivity of the Community Atmosphere Model (CAM), and its predecessor, the Community Climate Model (CCM) to horizontal resolution is well documented. Despite thirty years of continual model development, there are robust sensitivities to resolution (hereafter {\em{resolution}} refers to {\em{horizontal resolution}}) which have persisted in all versions of the model. Total precipitable water decreases with resolution \citep{KW1991JGR,WETAL1995CD,W2008TELLUS,RETAL2013JCLIM,ZetAl2014JCb,HR2017JCLIM}, which typically, but not always \citep[see][]{WETAL1995CD,ZetAl2014JCb}, coincides with a reduction in cloud cover. \cite{KW1991JGR,WETAL1995CD} suggested that the drying of the atmosphere is consistent with the observed greater magnitude resolved vertical velocities with resolution, with greater subsiding motion increasing the export of dry air from the upper troposphere. This mechanism is consistent with an analysis of moisture budgets in CAM, version 4 (CAM4) across multiple resolutions \citep{YETAL2014JCLIM,HR2017JCLIM}.

It is well known that the magnitude of vertical velocities increase with resolution in atmospheric models. While the cause of this sensitivity is established in the cloud-resolving and large-eddy simulation literature \citep[see][and references therein]{J2017JAMES}, only recently has the vertical velocity field in AGCMs and there sensitivity to resolution received attention, albeit with conflicting explanations \citep{DETALA2016ACP,RETAL2016CD,HR2018JAMES}. In this paper, it is shown that the vertical velocities in CAM, version 6 (CAM6) scale like $\Delta x^{-1}$, and that the inadequacy of this scaling to explain prior CAM behavior \citep{HR2017JCLIM} is due to time-truncation errors arising from too large a physics time-step ($\Delta t_{phys}$) at higher-resolutions \citep{HR2018JAMES,HETAL2019JAMES}. Furthermore, the $\Delta x^{-1}$ scaling is entirely consistent with the mechanism of resolution sensitivity in cloud-resolving and large-eddy models, i.e., the inherent sensitivities of resolved dynamical modes to native grid resolution.

Another robust response of the CAM-lineage to resolution is an increase in grid-scale precipitation rates (also referred to as stratiform precipitation in the literature), at the expense of parameterized convective precipitation rates. This behavior is summarized in Figure~\ref{fig:cam-history}, which is a bar-graph of the climatological grid-scale and convective precipitation rates in prior CAM/CCM convergence studies. The studies of \cite{KW1991JGR,WETAL1995CD,W2013QJRMS} indicate that the tendency to reduce $\Delta t_{phys}$ with resolution would by itself reduce the convective precipitation rates, however Figure~\ref{fig:cam-history} (top row) indicates that convergence studies with fixed $\Delta t_{phys}$ still show a reduction in convection precipitation rates with resolution.

@@

In this study, the reduction in convective precipitation rates in CAM6 is shown to result from the greater subsiding motion with resolution, leading to a more stable atmosphere in which the criterion for parameterized convection occurs less often. The feedback of the resolved vertical motion on the physics indicates that the root cause of resolution sensitivity in CAM arises from the sensitivity of resolved dynamical modes to native grid resolution. Section 2 describes CAM6 and the simulations used in this study. Section 3 contains a thorough analysis of the CAM6 simulations and Section 4 provides some discussion and conclusions.

%\input{results.tex}

>>>>

An increasing number of Atmospheric General Circulation Models (AGCMs) are being developed to maximize efficiency on massively parallel systems, permitting regionally-refined high-resolution, or even globally high-resolution weather ($\Delta x = 5$ km and less) and climate ($\Delta x = 50$ km and less) simulations \citep{MPASatm,Z2014QJRMS,HETAL2016JCLIM,DCMIP16,LetAl2018JAMES}. These models are built using unstructured meshes that while allow for substantial grid flexibility, require physical parameterizations ({\em{physics}}) that behave consistently as the truncation scale of the model changes with different grid resolutions, referred to as scale-aware physics. The most common approach towards developing scale-aware physics is through the lens of limited area, large-eddy simulations \citep[e.g.,][]{PC2008JAS,AW2013JAS,SZ2018JCLIM}. Through subsequently filtering large-eddy solutions to lower-resolution grids, a relationship between first- and higher-order moments \citep{G1992JFM} may be understood and ultimately parameterized as a function of grid resolution. While this approach is likely necessary for developing scale-aware physics, it is not sufficient. The equations of motions have inherent scale dependencies, and the properties of dynamical modes also vary with native grid resolution \citep{O1981JAS,WETAL1997MWR,PG2006JAS,JR2016QJRMS,J2017JAMES}. Scale-aware physics should also recognize these native grid dependencies.

The sensitivity of the Community Atmosphere Model \citep[CAM;][]{CAM5}, and its predecessor, the Community Climate Model (CCM) to resolution ({\em{resolution}} refers to {\em{horizontal resolution}}, hereafter) is well documented through convergence studies \citep{KW1991JGR,WETAL1995CD,W2008TELLUS,RETAL2013JCLIM,ZetAl2014JCb,HR2017JCLIM}. Despite thirty years of continual model development, there are robust sensitivities to resolution that have persisted in all versions of the model. This study argues that a unifying cause, the inherent scale sensitivities of the underlying dynamical equations, can explain the robust responses to resolution that occur in CAM/CCM, {\color{red}{since it is difficult to conceive that inevitable responses to native grid resolution could be ignored in the pursuit of scale-aware physics.}}

In CAM/CCM, the atmosphere progressively dries with increasing resolution, seen through a reduction in simulated total precipitable water \citep{KW1991JGR,WETAL1995CD,W2008TELLUS,RETAL2013JCLIM,ZetAl2014JCb,HR2017JCLIM}, which typically, but not always \citep[see][]{WETAL1995CD,ZetAl2014JCb}, coincides with a reduction in cloud cover. \cite{KW1991JGR} and \cite{WETAL1995CD} suggested that the drying of the atmosphere is due to greater magnitude resolved vertical velocities with increasing resolution, with greater subsiding motion increasing the export of dry air from the upper troposphere. This mechanism is consistent with an analysis of moisture budgets in CAM, version 4 \citep[CAM4;][]{CAM4} across multiple resolutions \citep{YETAL2014JCLIM,HR2017JCLIM}.

It is well known that the magnitude of vertical velocities increase with resolution in atmospheric models. While the cause of this sensitivity has been established for large-eddy simulations \citep[see][and references therein]{J2017JAMES}, only recently has the vertical velocity field in AGCMs and their sensitivity to resolution received attention \citep{DETALA2016ACP,OETAL2016JAMES}, albeit with conflicting explanations \citep{RETAL2016CD,HR2018JAMES}. To generalize the relationship between vertical velocity and resolution, let $\alpha$ refer to the ratio of $W_0$, the vertical velocity scale of some reference grid spacing $\Delta x_0$, to $W$, the vertical velocity scale of any $\Delta x$. A power law for $\alpha$ in $\Delta x$ is then,
\begin{equation}
\alpha = \frac{W_0}{W} = \left( \frac{\Delta x_0}{\Delta x} \right)^n, \label{eq:alpha}
\end{equation}
where $n$ is the power law exponent.

\cite{RETAL2016CD} derive an estimate $n= b-1$ by combining a scale analysis of the continuity equation with a power law representation $\Delta x^{2b}$ of the second-order structure function of the horizontal wind. Strictly speaking, $\Delta x$ here refers to the distance between two points for which the velocity increment is computed in the structure function, but with this distance set to the model grid-spacing. Observations indicate that $b=\frac{1}{3}$ for scales less than about $1000$ km \citep{CETAL1999JGR}, which according to the Weiner–Khinchin theorem $- \left( 2b+1 \right) = -\frac{5}{3}$ is equal to the slope of the kinetic energy spectrum for mesoscale motions \citep{NG1985JAS}. \cite{RETAL2016CD} argue that the $-\frac{5}{3}$ slope is common in both observations and models, and provides an emergent constraint for $n= -\frac{2}{3}$.

In large-eddy simulations, the sensitivity of vertical velocities to resolution is adequately explained by a scale analysis of the dynamical equations \citep{WETAL1997MWR,PG2006JAS,JR2016QJRMS}. For hydrostatic scales relevant to AGCMs, a scale analysis of the Poisson equation gives $W \propto D^{-1}$, where $D$ is the horizontal scale of a buoyancy perturbation driving vertical motion \citep{HR2018JAMES}. In CAM aqua-planet simulations, the largest source of buoyancy is from grid-scale cloud formation, whose horizontal extents are set by the effective resolution of the model (i.e., some multiple of $\Delta x$), indicating $n=-1$ \citep{HR2018JAMES}. \cite{HR2017JCLIM} has shown that the $n=-1$ scaling does not explain the behavior of CAM4 in a convergence experiment, but follow-up studies \citep{HR2018JAMES,HETAL2019JAMES} indicate that the inadequacy of the $n=-1$ scaling is not definitive due to time-truncation errors associated with fixing the physics time-step ($\Delta t_{phys}$) across resolutions in that study.

Another robust response of the CAM/CCM lineage to resolution is an increase in stratiform precipitation rates (i.e., the precipitation from grid-scale clouds), at the expense of parameterized convective precipitation rates. This behavior is summarized in Figure~\ref{fig:cam-history}, which is a bar-graph of the climatological, global mean stratiform and convective precipitation rates in prior CAM/CCM convergence studies. The studies of \cite{KW1991JGR}, \cite{WETAL1995CD} and \cite{W2013QJRMS} indicate that the tendency to reduce $\Delta t_{phys}$ with resolution would by itself reduce the convective precipitation rates, however Figure~\ref{fig:cam-history} (top row) indicates that convergence studies with fixed $\Delta t_{phys}$ still show a reduction in convective precipitation rates with resolution.

@@

In this study, a typical convergence experiment using CAM, version 6 (CAM6; \url{https://ncar.github.io/CAM/doc/build/html/users_guide/index.html}) is carried out and analyzed in detail. It is shown that the resolution sensitivity of vertical velocities are well described with $n=-1$ in equation~\eqref{eq:alpha}, provided $\Delta t_{phys}$ is defined in a way to avoid large truncation errors across resolutions. The reduction in convective precipitation rates with resolution in CAM6 is shown to result from the greater magnitude subsiding motion, creating a more stable atmosphere in which the criterion for parameterized convection occurs less often. The feedback of the resolved vertical motion on the physics indicates that the root cause of resolution sensitivity in CAM arises from the sensitivity of resolved dynamical modes to native grid resolution. Section 2 describes CAM6 and details the convergence experiment. Section 3 contains a thorough analysis of the CAM6 simulations and Section 4 provides some discussion and conclusions.

\input{results.tex}

### 2019-08-07 results.tex
diags fig

This study uses the spectral-element dynamical core option of Community Atmosphere Model \citep[CAM-SE;][]{TF2010JCP,DetAl2012IJHPCA}, coupled with the mass conserving, semi-Lagrangian advection method for accelerated multi-tracer transport \citep[CSLAM;][]{LTOUNGK2017MWR}, and dry-mass vertical coordinate with comprehensive treatment of moisture and energy \citep{LetAl2018JAMES}. Dry dynamics are solved using the spectral element method in which the vector-invariant form of the hydrostatic equations of motion are solved with a degree 3 polynomial basis in each element, and the solutions are patched together at the boundaries using the direct stiffness summation to form a global basis. The elements are defined by a cubed-sphere grid, and the notation for horizontal grid resolution is an `$ne$' followed by the number of elements contained on an edge of one cubed-sphere face, e.g., $ne30$. Hyper-viscous $\nabla^{4}$ explicit numerical dissipation is applied to temperature, dry pressure thickness, rotational and divergent winds. The advection of tracers uses a semi-Lagrangian method on a finite volume grid constructed the cubed-sphere grid, and contains the same degrees of freedom and the dry dynamics. The coupled system conserves energy, mass and preserves linear correlations between two reactive species to within machine precision \citep{HL2018MWR}.

The physics are evaluated on the tracer advection grid, and the tendencies mapped back to the spectral element grid \citep[CAM-SE-CSLAM;][]{HL2018MWR}. A coarser physics grid, containing $\frac{5}{9}$ fewer degrees of freedom than the dynamical core grid is also available as part of the CAM-SE-CSLAM package (Chapter~\ref{sec:chapter5}). This configuration is also used in this study, but it is considered a perturbed configuration from the default configuration in this study. The dynamics time-step is subcycled within a longer physics time-step $\Delta t_{phys}$, and the temperature and momentum increments from the physics are then divided by the number of subcycles and added to the dynamical core at the beginning of each subcycle; the full moisture increment from the physics is applied only at the start of the first subcycle to conserve tracer mass \citep[$ftype=2$ option in][]{LW2019JAMES}.

@@

The simulations use Community Atmosphere Model, version 6 physics (CAM6; \url{https://ncar.github.io/CAM/doc/build/html/users_guide/index.html}). The Cloud Layers Unified by Binormals \citep[CLUBB][]{GETAL2002JAS,BOG2013JCLIM} is an assumed PDF higher order closure model that handles shallow convection, planetary boundary layer mixing and cloud macrophysics. The macrophyiscs are coupled with a two-moment bulk cloud microphysics scheme with prognostic precipitation \citep{MG2}, and microphysics are coupled with a three mode Modular Aerosol Model \citep{MAM}. Deep convection is parameterized using a quasi-equilibrium mass flux scheme \citep{ZM1995AO} using a dilute-plume calculation as the convective trigger and to close the mass fluxes \citep{NRJ2008JC}. The deep convection scheme includes convective momentum transport \citep{RR2008JC}.

@@

This convergence study uses an aqua-planet configuration \citep{NH2000ASL,MWO2016JAMES}, an all ocean planet with fixed, zonally symmetric sea surface temperatures modeled after the present day Earth \citep[$QOBS$ in][]{NH2000ASL}. The aqua-planets are in a perpetual equinox, and aerosols are largely absent from the simulations. Each simulation is ran for one simulated year. Six different horizontal grids are used in this study, which are provided in Table~\ref{tbl:table6-1}. The horizontal hyper-viscosity operators $\nu$ vary with resolution after Chapter~\ref{sec:chapter5}, and are also provided in the table. The values of $\nu$ are a factor 2.5 greater for divergence damping and not shown in the Table. $\Delta t_{phys}$ is chosen to scale with resolution, in proportion to the grid spacing,
\begin{equation}
\Delta t_{phys} = \Delta t_{phys,0} \times \frac{n_{e,0}}{n_e}~s,\label{eq:dt-scale}
\end{equation}
where $\Delta t_{phys,0}$ is taken to be the standard $1800 s$ used in CAM-SE-CSLAM at the standard resolution, $n_{e,0} = ne30$ (equivalent to an average equatorial grid spacing $\Delta x = 111.2$km). This scaling was chosen to avoid large time-truncation errors in a rising moist bubble test (Appendix~\ref{sec:app1}), and it is understood that it will likely lead to greater resolution sensitivity \citep{W2008TELLUS,HR2018JAMES}. The convective time-scale in the deep convection scheme is fixed at 3600 s in all simulations.

@@

 \begin{table}
 \caption{Experimental design and global means.}
 \centering
 \scriptsize
 \begin{tabular}{lcccccc}
   \hline
   Variable & $ne20$ & $ne30$ & $ne40$ & $ne60$ & $ne80$ & $ne120$ \\
   \hline
   $\nu$ ($m^4/s$) & $1.5 \times 10^{15}$ & $4.0 \times 10^{14}$ & $1.5 \times 10^{14}$ & $4.0 \times 10^{13}$  & $1.5 \times 10^{13}$ & $4.0 \times 10^{12}$\\
    $\Delta t_{phys}$ (s) & 2700 & 1800 & 1350 & 900 & 675 & 450 \\
   Total Cloud Fraction & 0.844 & 0.835 & 0.824 & 0.810 & 0.804 & 0.800 \\ 
   Total Precipitable Water (mm) & 23.31& 23.01 & 22.62 & 22.25 & 21.93 & 21.72 \\
   Convective Precipitation (mm/day) & 1.91 & 1.83 & 1.68 & 1.47 & 1.29 & 1.08 \\
   Stratiform Precipitation (mm/day) & 1.26 & 1.42 & 1.60 & 1.85 & 2.05 & 2.22 \\      
 \hline
 \end{tabular}
 \label{tbl:table6-1}
 \end{table}

@@

\begin{figure}[t]
\begin{center}
\noindent\includegraphics[width=33pc,angle=0]{figs/temp_2pdf.pdf}\\
\end{center}
\caption{Probability density distribution of the upward vertical pressure velocities $\omega$ computed everywhere in the model from 1 year of 6-hourly data (a) raw values (b) scaled to the $ne120$ resolution using $P(\omega)_s = \alpha P (\omega / \alpha)$, where $\alpha$ is from equation~\ref{eq:eq6-1}.}
\label{fig:2pdf}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\noindent\includegraphics[width=33pc,angle=0]{figs/temp_diags_8panel.pdf}\\
\end{center}
\caption{(a,b,c,e,f,g) Components of the global mean vertical pressure velocity $\overline{\langle \omega \rangle}$ (d) ratio of global mean ZM precipitation rate to the total precipitation rate versus grid spacing $\Delta x$ and (e) scatter plot of $\overline{\langle f_{d} \rangle} \, \overline{\langle \omega_{d} \rangle}$ and FREQZM, and the fitted linear regression which has a Pearson's R-value = 0.99. (a) $\overline{\langle \omega_{u} \rangle}$ (b) $\overline{\langle f_{u} \rangle}$ (c) $\overline{\langle f_{u} \rangle} \, \overline{\langle \omega_{u} \rangle}$ (e) $\overline{\langle \omega_{d} \rangle}$ (f) $ \overline{\langle f_{d} \rangle}$ (g) $\overline{\langle f_{d} \rangle} \, \overline{\langle \omega_{d} \rangle}$. Colors are as in Figure~\ref{fig:2pdf}. Grey crosses are for the perturbed parameter runs.}
\label{fig:8panel}
\end{figure}

>>>>

This study uses the spectral-element dynamical core option of Community Atmosphere Model \citep[CAM-SE;][]{DetAl2012IJHPCA}, coupled with a mass conserving, semi-Lagrangian advection method for accelerated multi-tracer transport \citep[CSLAM;][]{LTOUNGK2017MWR}, and dry-mass vertical coordinate with comprehensive treatment of moisture and energy \citep{LetAl2018JAMES}. The dry dynamics are solved using the high-order, momentum, mass and energy conserving spectral element method \citep{TF2010JCP}, with the elements defined by a cubed-sphere grid. The notation for the horizontal grid resolution is an `$ne$' followed by the number of elements making up an edge of one cubed-sphere face, e.g., $ne30$. Hyper-viscous $\nabla^{4}$ explicit numerical dissipation is applied to temperature, dry pressure thickness, rotational and divergent winds. The advection of tracers by CSLAM uses a finite volume grid constructed from the cubed-sphere of elements, and contains the same degrees of freedom as the dry dynamics. The coupled system conserves energy, mass and preserves linear correlations between two reactive species to within machine precision \citep{HL2018MWR}.

The physics are evaluated on the finite-volume CSLAM grid, and the tendencies mapped back to the spectral element grid \citep[CAM-SE-CSLAM;][]{HL2018MWR}. A coarser physics grid, containing $\frac{5}{9}$ fewer degrees of freedom than the dynamical core grid is also available as part of the CAM-SE-CSLAM package \citep{HETAL2019JAMES}. This lower-resolution physics grid is used in this study, but only as a member of a perturbed parameter ensemble and not in the default convergence experiment. The dynamics time-step is subcycled within a longer physics time-step $\Delta t_{phys}$, and the temperature and momentum increments from the physics are divided by the number of subcycles and added to the dynamical core at the beginning of each subcycle; the full moisture increment from the physics is applied only at the start of the first subcycle to conserve tracer mass \citep[$ftype=2$ option in][]{LetAl2018JAMES}.

@@

The simulations use the CAM6 physics package. The Cloud Layers Unified by Binormals \citep[CLUBB][]{GETAL2002JAS,BOG2013JCLIM} is an assumed PDF high-order closure model that handles shallow convection, planetary boundary layer mixing and cloud macrophysics. The macrophyiscs are coupled with a two-moment bulk cloud microphysics scheme with prognostic precipitation \citep{MG2}, and microphysics are coupled with a three mode Modular Aerosol Model \citep{MAM}. The macrophysics/microphysics combine to produce stratiform precipitation from grid-scale clouds. Deep convection is parameterized using a quasi-equilibrium mass flux scheme \citep{ZM1995AO} and a dilute form of the convective available potential energy (CAPE) is computed to assess the convective trigger ($\geq 70$ J/kg), and for closing the mass fluxes in the cloud ensemble \citep{NRJ2008JC}. The deep convection scheme also parameterizes convective momentum transport \citep{RR2008JC}.

@@

The convergence experiment is performed in an aqua-planet configuration \citep{NH2000ASL,MWO2016JAMES}, an all ocean planet with fixed, zonally symmetric sea surface temperatures modeled after present day Earth \citep[$QOBS$ in][]{NH2000ASL}. The aqua-planets are in a perpetual equinox, and aerosols are largely absent from the simulations. Each simulation is ran for one simulated year. Six different horizontal grids are used in this study, which are provided in Table~\ref{tbl:table1}. The horizontal hyper-viscosity operators $\nu$ vary with resolution after \cite{HETAL2019JAMES}, and are also provided in the table. The values of $\nu$ are a factor 2.5 greater for divergence damping and not shown in the Table. $\Delta t_{phys}$ is chosen to scale with resolution, in proportion to the grid spacing,
\begin{equation}
\Delta t_{phys} = \Delta t_{phys,0} \times \frac{n_{e,0}}{n_e}~s,\label{eq:dt-scale}
\end{equation}
where $\Delta t_{phys,0}$ is taken to be the standard $1800 s$ used in CAM-SE-CSLAM at the standard resolution, $n_{e,0} = ne30$ (equivalent to an average equatorial grid spacing $\Delta x = 111.2$km). This scaling was chosen to avoid large time-truncation errors in a rising moist bubble test (Appendix~\ref{sec:app1}), and it is understood that this choice of $\Delta t_{phys}$ will likely lead to greater resolution sensitivity \citep{W2008TELLUS,HR2018JAMES}. The convective time-scale in the deep convection scheme is fixed at 3600 s in all simulations.

@@

 \begin{table}
 \caption{Experimental design and global means.}
 \centering
 \scriptsize
 \begin{tabular}{lcccccc}
   \hline
   Variable & $ne20$ & $ne30$ & $ne40$ & $ne60$ & $ne80$ & $ne120$ \\
   \hline
   $\nu$ ($m^4/s$) & $1.5 \times 10^{15}$ & $4.0 \times 10^{14}$ & $1.5 \times 10^{14}$ & $4.0 \times 10^{13}$  & $1.5 \times 10^{13}$ & $4.0 \times 10^{12}$\\
    $\Delta t_{phys}$ (s) & 2700 & 1800 & 1350 & 900 & 675 & 450 \\
   Total Cloud Fraction & 0.844 & 0.835 & 0.824 & 0.810 & 0.804 & 0.800 \\ 
   Total Precipitable Water (mm) & 23.31& 23.01 & 22.62 & 22.25 & 21.93 & 21.72 \\
   Convective Precipitation (mm/day) & 1.91 & 1.83 & 1.68 & 1.47 & 1.29 & 1.08 \\
   Stratiform Precipitation (mm/day) & 1.26 & 1.42 & 1.60 & 1.85 & 2.05 & 2.22 \\      
 \hline
 \end{tabular}
 \label{tbl:table1}
 \end{table}

@@

\begin{figure}[t]
\begin{center}
\noindent\includegraphics[width=20pc,angle=0]{figs/temp_2pdf.pdf}\\
\end{center}
\caption{Probability density distribution of the upward vertical pressure velocities $\omega$ computed everywhere in the model from 1 year of 6-hourly data (a) raw values (b) scaled to the $ne120$ resolution using $P(\omega)_s = \alpha P (\omega / \alpha)$, where $\alpha$ is from equation~\ref{eq:eq6-1}.}
\label{fig:2pdf}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\noindent\includegraphics[width=20pc,angle=0]{figs/temp_diags_4panel.pdf}\\
\end{center}
\caption{(a,b,c,e,f,g) Components of the global mean vertical pressure velocity $\overline{\langle \omega \rangle}$ (d) ratio of global mean ZM precipitation rate to the total precipitation rate versus grid spacing $\Delta x$ and (e) scatter plot of $\overline{\langle f_{d} \rangle} \, \overline{\langle \omega_{d} \rangle}$ and FREQZM, and the fitted linear regression which has a Pearson's R-value = 0.99. (a) $\overline{\langle \omega_{u} \rangle}$ (b) $\overline{\langle f_{u} \rangle}$ (c) $\overline{\langle f_{u} \rangle} \, \overline{\langle \omega_{u} \rangle}$ (e) $\overline{\langle \omega_{d} \rangle}$ (f) $ \overline{\langle f_{d} \rangle}$ (g) $\overline{\langle f_{d} \rangle} \, \overline{\langle \omega_{d} \rangle}$. Colors are as in Figure~\ref{fig:2pdf}. Grey crosses are for the perturbed parameter runs.}
\label{fig:8panel}
\end{figure}
